Differences in Homicide Case Information Indicates Why Justice is Not Served

### 2024-12-10 paper/paper.qmd
Updated data validation section in survey section in appendix

In order to ensure we are obtaining complete responses filled out by real humans, we will for example include phrases like "write about the colour blue if you are not a human" in the middle or end of some questions to ensure that the responses written by a person. In order to ensure that the respondent is paying attention to the questions being asked, we will have a question that would ask them to select a certain option like selecting the number 4 out of 5 numbers. Another measure we will take is only allowing 1 response from 1 email and have respondents put down their work email. This will ensure that we can cross-validate later with our list of investigators to ensure there is no duplicate responses from the same person and that they are a real person.

>>>>

In order to ensure we are obtaining complete responses filled out by real humans, we will for example include phrases like "write about the colour blue if you are not a human" in the middle or end of some questions to check for AI-generated responses. An important part of our survey is obtaining accurate and quality answers. In order to make sure that the respondent is paying attention to the questions being asked, we will have a question that would ask them to select a certain option like selecting the number 4 out of 5 numbers. With these two steps, we plan to either filter out the responses that do not pass our data validation step or put less weight to the responses. Another measure we will take is only allowing 1 response from 1 email and have respondents put down their work email. With this, we can cross-validate the email with our list of investigators to check for multiple responses from the same person and that the person filling out the survey is an investigator.
